Quantum Mechanics Assignment One

### 2016-10-03 em/latex/HW1.tex
Finish HW1? Probably needs checking.

>>>>

\section{Problem Two}
\textbf{Part A}\\
We want to show the following equality is always true:

\begin{align*}
  \int\rho_1\phi_2d^3\vec{r} &= \int\rho_2\phi_1d^3\vec{r}
\end{align*}

We first apply the Laplace Equation:

\begin{align*}
  -\epsilon_0\int\nabla^2\phi_1\phi_2d^3\vec{r} &= -\epsilon_0\int\nabla^2\phi_2\phi_1d^3\vec{r}
\end{align*}

We then expand this equation into its cartesian representation:

\begin{align*}
  \int\int\int\sum_{n=x,y,z}\frac{\partial^2}{\partial n^2} (\phi_1) \phi_2 dxdydz &=
  \int\int\int\sum_{n=x,y,z}\frac{\partial^2}{\partial n^2} (\phi_2) \phi_1 dxdydz
\end{align*}

We then use Integration by Parts:

\begin{align*}
  \int\int\int\sum_{n=x,y,z}\left(\frac{d}{dn}\phi_1\phi_2\Big|_{-\infty}^{\infty} - \int\frac{\partial}{\partial n}\phi_1\frac{\partial}{\partial n}\phi_2dn \right) dxdydz &=
  \int\int\int\sum_{n=x,y,z}\left(\frac{d}{dn}\phi_2\phi_1\Big|_{-\infty}^{\infty} - \int\frac{\partial}{\partial n}\phi_2\frac{\partial}{\partial n}\phi_1dn \right) dxdydz
\end{align*}

We define our voltages to be zero at infinity, so the UV term of the integration by parts goes to zero, leaving us with:

\begin{align*}
  -\int\int\int\sum_{n=x,y,z}\left(\int\frac{\partial}{\partial n}\phi_1\frac{\partial}{\partial n}\phi_2dn \right) dxdydz &=
  -\int\int\int\sum_{n=x,y,z}\left(\int\frac{\partial}{\partial n}\phi_2\frac{\partial}{\partial n}\phi_1dn \right) dxdydz
\end{align*}

We see that these expressions are identical since multiplication is commutative, thus the initial statement must be true.
\textbf{Part B}\\

We define the voltage on conductor A as: $V_A = V_{AA} + V_{BA}$ where $V_{BA}$ is the potential due to conductor B. We define $V_{AB}$ as the potential on B due to A. We let $\rho_A$ and $\rho_B$ be the charge distributions on A and B respectively, where $\int\rho_AdV = \int\rho_BdV = Q$. We begin with Green's Reciprocity theorem:

\begin{align*}
  \int V_{AB}(\vec{R})\rho_A(\vec{r})dV &= \int V_{BA}(\vec{r})\rho_B(\vec{r})dV\\
\end{align*}

Because A and B are conductors, we know that their potentials $V_{AB}$ and $V{BA}$ are constant. Thus we can remove them from the integral:

\begin{align*}
  V_{AB}\int\rho_A(\vec{r})dV &= V_{BA}\int\rho_B(\vec{r})dV\\
  V_{AB}Q &= V_{BA}Q\\
\end{align*}

Thus $V_{AB} = V_{BA}$. From this we can see that $V_A = V_{AA} + V_{AB}$.\\

NOTE: $V_{A} = V_{AA} + V_{AB}$ is constant, but is $V_{AB}$ constant?\\
